Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-01-16 paper.qmd
Updated Figure 14 with more bins

<!--Fit the best model for author suggestion and compute error-->
```{r}
#| label: hexbin-pbmc
## Compute hexbin parameters
num_bins_x_pbmc <- 26
lim1 <- pbmc_scaled_obj$lim1
lim2 <- pbmc_scaled_obj$lim2
r2_pbmc <- diff(lim2)/diff(lim1)

@@

<!--Fit the best model and compute error-->
```{r}
#| label: num-bins-pbmc
## Compute hexbin parameters
num_bins_x_pbmc <- 13
lim1 <- pbmc_scaled_obj$lim1
lim2 <- pbmc_scaled_obj$lim2
r2_pbmc <- diff(lim2)/diff(lim1)

@@

distance_df_small_edges_pbmc <- distance_pbmc |>
  filter(distance < benchmark_pbmc) |>
  filter(!(row_number() %in% c(6, 12, 14, 16, 17, 19, 23, 29, 30, 143, 144, 146, 147, 157)))

>>>>

<!--Fit the best model for author suggestion and compute error-->
```{r}
#| label: hexbin-pbmc
## Compute hexbin parameters
num_bins_x_pbmc <- 60
lim1 <- pbmc_scaled_obj$lim1
lim2 <- pbmc_scaled_obj$lim2
r2_pbmc <- diff(lim2)/diff(lim1)

@@

<!--Fit the best model and compute error-->
```{r}
#| label: num-bins-pbmc
## Compute hexbin parameters
num_bins_x_pbmc <- 30
lim1 <- pbmc_scaled_obj$lim1
lim2 <- pbmc_scaled_obj$lim2
r2_pbmc <- diff(lim2)/diff(lim1)

@@

distance_df_small_edges_pbmc <- distance_pbmc |>
  filter(distance < benchmark_pbmc) #|>
  #filter(!(row_number() %in% c(6, 12, 14, 16, 17, 19, 23, 29, 30, 143, 144, 146, 147, 157)))
